CF Registry Analysis

### 2022-12-27 Christine Chan/CF Registry/cf_registry_analysis.qmd
Update cf_registry_analysis.qmd

```{r}
#| label: tbl-incidence_cffpr
#| tbl-cap: "Year-on-Year Incidence of CFRD Based on CFFPR Alone"
# For each year, pull everyone with and without CFRD that year
year_inc = function(df=encounter,year,py = 1000){
  # Filter and count
  inc = df %>%  
    filter(reviewyear==year,is.na(first_cfrd_cffpr) | first_cfrd_cffpr == year) %>%
    group_by(eDWID) %>% filter(row_number() == 1) %>% 
    select(eDWID,`Age Group 2018`,cfrd_cffpr)
  inc = inc %>% group_by(cfrd_cffpr) %>% count(`Age Group 2018`,.drop = F)
  # Calculations
  new_cases = sum(inc$n[inc$cfrd_cffpr=="Yes"])
  total_at_risk = sum(inc$n)
  total_inc = new_cases/(total_at_risk/py)

  new_cases_10 = sum(inc$n[inc$cfrd_cffpr=="Yes" & inc$`Age Group 2018` == "< 10"])
  at_risk_10 = sum(inc$n[inc$`Age Group 2018` == "< 10"])
  inc_10 = new_cases_10/(at_risk_10/py)

  new_cases_10_18 = sum(inc$n[inc$cfrd_cffpr=="Yes" & inc$`Age Group 2018` == "10 - 18"])
  at_risk_10_18 = sum(inc$n[inc$`Age Group 2018` == "10 - 18"])
  inc_10_18 = new_cases_10_18/(at_risk_10_18/py)

  new_cases_19_30 = sum(inc$n[inc$cfrd_cffpr=="Yes" & inc$`Age Group 2018` == "19 - 30"])
  at_risk_19_30 = sum(inc$n[inc$`Age Group 2018` == "19 - 30"])
  inc_19_30 = new_cases_19_30/(at_risk_19_30/py)

  new_cases_30 = sum(inc$n[inc$cfrd_cffpr=="Yes" & inc$`Age Group 2018` == "> 30"])
  at_risk_30 = sum(inc$n[inc$`Age Group 2018` == "> 30"])
  inc_30 = new_cases_30/(at_risk_30/py)

@@

```{r}
#| label: tbl-incidence_both
#| tbl-cap: "Year-on-Year Incidence of CFRD Based on CFFPR and OGTT"
# For each year, pull everyone with and without CFRD that year
year_inc = function(df=encounter,year,py = 1000){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,is.na(first_cfrd_both) | first_cfrd_both == year) %>%
    group_by(eDWID) %>% filter(row_number() == 1) %>%
    select(eDWID,reviewyear,encounternum,`Age Group 2018`,
           twohour_bloodglucose,cfrd_both,first_cfrd_both)
  inc = inc %>% group_by(cfrd_both) %>% count(`Age Group 2018`,.drop = F)
  # Calculations
  new_cases = sum(inc$n[inc$cfrd_both=="Yes"])
  total_at_risk = sum(inc$n)
  total_inc = new_cases/(total_at_risk/py)

  new_cases_10 = sum(inc$n[inc$cfrd_both=="Yes" & inc$`Age Group 2018` == "< 10"])
  at_risk_10 = sum(inc$n[inc$`Age Group 2018` == "< 10"])
  inc_10 = new_cases_10/(at_risk_10/py)

  new_cases_10_18 = sum(inc$n[inc$cfrd_both=="Yes" & inc$`Age Group 2018` == "10 - 18"])
  at_risk_10_18 = sum(inc$n[inc$`Age Group 2018` == "10 - 18"])
  inc_10_18 = new_cases_10_18/(at_risk_10_18/py)

  new_cases_19_30 = sum(inc$n[inc$cfrd_both=="Yes" & inc$`Age Group 2018` == "19 - 30"])
  at_risk_19_30 = sum(inc$n[inc$`Age Group 2018` == "19 - 30"])
  inc_19_30 = new_cases_19_30/(at_risk_19_30/py)

  new_cases_30 = sum(inc$n[inc$cfrd_both=="Yes" & inc$`Age Group 2018` == "> 30"])
  at_risk_30 = sum(inc$n[inc$`Age Group 2018` == "> 30"])
  inc_30 = new_cases_30/(at_risk_30/py)

>>>>

```{r}
#| label: tbl-incidence_cffpr
#| tbl-cap: "Year-on-Year Incidence of CFRD Based on CFFPR Alone"
# For each year, pull everyone with and without CFRD that year
year_inc = function(df=encounter,year,py = 1000){
  # Filter and count
  inc = df %>%  
    filter(reviewyear==year,is.na(first_cfrd_cffpr) | first_cfrd_cffpr == year) %>%
    group_by(eDWID) %>% filter(row_number() == 1) %>% 
    select(eDWID,`Age Group`,cfrd_cffpr)
  inc = inc %>% group_by(cfrd_cffpr) %>% count(`Age Group`,.drop = F)
  # Calculations
  new_cases = sum(inc$n[inc$cfrd_cffpr=="Yes"])
  total_at_risk = sum(inc$n)
  total_inc = new_cases/(total_at_risk/py)

  new_cases_10 = sum(inc$n[inc$cfrd_cffpr=="Yes" & inc$`Age Group` == "< 10"])
  at_risk_10 = sum(inc$n[inc$`Age Group` == "< 10"])
  inc_10 = new_cases_10/(at_risk_10/py)

  new_cases_10_18 = sum(inc$n[inc$cfrd_cffpr=="Yes" & inc$`Age Group` == "10 - 18"])
  at_risk_10_18 = sum(inc$n[inc$`Age Group` == "10 - 18"])
  inc_10_18 = new_cases_10_18/(at_risk_10_18/py)

  new_cases_19_30 = sum(inc$n[inc$cfrd_cffpr=="Yes" & inc$`Age Group` == "19 - 30"])
  at_risk_19_30 = sum(inc$n[inc$`Age Group` == "19 - 30"])
  inc_19_30 = new_cases_19_30/(at_risk_19_30/py)

  new_cases_30 = sum(inc$n[inc$cfrd_cffpr=="Yes" & inc$`Age Group` == "> 30"])
  at_risk_30 = sum(inc$n[inc$`Age Group` == "> 30"])
  inc_30 = new_cases_30/(at_risk_30/py)

@@

```{r}
#| label: tbl-incidence_both
#| tbl-cap: "Year-on-Year Incidence of CFRD Based on CFFPR and OGTT"
# For each year, pull everyone with and without CFRD that year
year_inc = function(df=encounter,year,py = 1000){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,is.na(first_cfrd_both) | first_cfrd_both == year) %>%
    group_by(eDWID) %>% filter(row_number() == 1) %>%
    select(eDWID,reviewyear,encounternum,`Age Group`,
           twohour_bloodglucose,cfrd_both,first_cfrd_both)
  inc = inc %>% group_by(cfrd_both) %>% count(`Age Group`,.drop = F)
  # Calculations
  new_cases = sum(inc$n[inc$cfrd_both=="Yes"])
  total_at_risk = sum(inc$n)
  total_inc = new_cases/(total_at_risk/py)

  new_cases_10 = sum(inc$n[inc$cfrd_both=="Yes" & inc$`Age Group` == "< 10"])
  at_risk_10 = sum(inc$n[inc$`Age Group` == "< 10"])
  inc_10 = new_cases_10/(at_risk_10/py)

  new_cases_10_18 = sum(inc$n[inc$cfrd_both=="Yes" & inc$`Age Group` == "10 - 18"])
  at_risk_10_18 = sum(inc$n[inc$`Age Group` == "10 - 18"])
  inc_10_18 = new_cases_10_18/(at_risk_10_18/py)

  new_cases_19_30 = sum(inc$n[inc$cfrd_both=="Yes" & inc$`Age Group` == "19 - 30"])
  at_risk_19_30 = sum(inc$n[inc$`Age Group` == "19 - 30"])
  inc_19_30 = new_cases_19_30/(at_risk_19_30/py)

  new_cases_30 = sum(inc$n[inc$cfrd_both=="Yes" & inc$`Age Group` == "> 30"])
  at_risk_30 = sum(inc$n[inc$`Age Group` == "> 30"])
  inc_30 = new_cases_30/(at_risk_30/py)
